La Palma Earthquakes

### 2025-03-27 Quarto/paper.qmd
test changes
Fix generated site

---
title: La Palma Earthquakes
author:
  - name: Steve Purves
    orcid: 0000-0002-0760-5497
    corresponding: true
    email: steve@curvenote.com
    roles:
      - Investigation
      - Project administration
      - Software
      - Visualization
    affiliations:
      - Curvenote
  - name: Rowan Cockett
    orcid: 0000-0002-7859-8394
    corresponding: false
    roles: []
    affiliations:
      - Curvenote
keywords:
  - La Palma
  - Earthquakes
abstract: |
  In September 2021, a significant jump in seismic activity on the island of La Palma (Canary Islands, Spain) signaled the start of a volcanic crisis that still continues at the time of writing. Earthquake data is continually collected and published by the Instituto Geográphico Nacional (IGN). ...
plain-language-summary: |
  Earthquake data for the island of La Palma from the September 2021 eruption is found ...
key-points:
  - A web scraping script was developed to pull data from the Instituto Geogràphico Nacional into a machine-readable form for analysis
  - Earthquake events on La Palma are consistent with the presence of both mantle and crustal reservoirs.
date: last-modified
citation:
  container-title: Earth and Space Science
---

@@

>>>>

---
title: La Palma Earthquakes
author:
  - name: Steve Purves
    orcid: 0000-0002-0760-5497
    corresponding: true
    email: steve@curvenote.com
    roles:
      - Investigation
      - Project administration
      - Software
      - Visualization
    affiliations:
      - Curvenote
  - name: Rowan Cockett
    orcid: 0000-0002-7859-8394
    corresponding: false
    roles: []
    affiliations:
      - Curvenote
keywords:
  - La Palma
  - Earthquakes
abstract: |
  In September 2021, a significant jump in seismic activity on the island of La Palma (Canary Islands, Spain) signaled the start of a volcanic crisis that still continues at the time of writing. Earthquake data is continually collected and published by the Instituto Geográphico Nacional (IGN). ...
date: last-modified
citation:
  container-title: Earth and Space Science
---

@@

Test update

<!-- This shouldnt be seen, its a comment -->
